### 2024-04-23 paper/paper.qmd
Initial commit

---
title: "Pursuit of Happiness"
subtitle: "The impact of growing Western criticism on Chinese Wellbeing"
author: 
  - Alexander Sun
thanks: "Code and data are available at: https://github.com/alexandersunliang/china_wellbeing.git"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(arrow)
library(here)
library(modelsummary)
library(knitr)
library(kableExtra)
wvsdata <- read_parquet(here("data/analysis_data/analysis_data2018.parquet"))
```

# Introduction

Since the early 1990s, China's economy has grown significantly, with an average annual GDP growth rate of around 10%. The 1990s market reforms aimed to control capitalism, showing that socialism could harness capitalist growth to increase national power. Today, China is a global economic leader, second only to the US in GDP; however, it is essential to assess how these changes affect societal well-being. Studies present mixed views on the effects of socialism and democracy. Cheung and Leung (2007) found that collectivism significantly impacts the well-being of the Chinese, whereas Hofstede (1980) observed that individualism encourages economic growth. Moore (2005) argued that the freedoms introduced in the 1980s led the Chinese towards a strong form of individualism, which starkly contrasts with the collectivist approach of the Cultural Revolution. Steele and Lynch examined whether individualist or collectivist traits prevail in modern China and their impact on subjective well-being (SWB). They focused on how these orientations predict SWB and if their influence has shifted as China transitioned towards a market economy.

While Steele and Lynch researched the impacts of the reform, this paper will attempt to reframe their ideas with a focus on the impacts of COVID-19. This study will replicate and extend Steele and Lynch’s previous research by examining the prevailing sentiments—individualist versus collectivist—in China post-COVID-19 in 2022 and their implications for SWB. We analyze whether and how the relationship between these cultural orientations and well-being has evolved in the context of China's continued economic and social transformations.

In this project, the estimand will be the difference in happiness level between each participant based on information like national pride, government support, and age.

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Data Source

To replicate the paper by Steele and Lynch, we obtained our data from the World Values Survey. While Steele and Lynch used time series data from three surveys (1990, 2001, 2007), we aim to look at more recent trends so we will include the World Values Survey data obtained from their 2018 wave. To be included into the survey dataset, countries must meet a minimum of 1200 entries. Since the survey is global, general guidelines are provided to the teams that are responsible for each country, but slight alterations in sampling method were permitted. The most common method of data collection consisted of face-to-face interviews with respondents at their home, and the answers were recorded on a paper questionnaire for later processing. For China, participants were chosen through probability sampling. The initial dataset contained 94278 responses and 606 variables, but after filtering for responses from China and removing non-responses, we are left with 3036 observations. Each wave of the survey is slightly different, so the wording of some questions and answers may vary.

## Variables

The original questionnaire was composed of approximately 300 questions, but for the purposes of our study we will focus on the following:

 - **Happiness**: Our dependent variable was measured as "life satisfaction" in the questionnaire. Participants responded with how happy they were with their current lifestyle on a scale of 1-10 with 1 being "completely dissatisfied" and 10 being "completely satisfied". We will later conduct a model to estimate this value based off our other regressors.

 - **National Pride**: Respondents were asked about their national pride with the question, "How proud are you to be Chinese?" We believe that this is especially important as it allows us to see temporal trends in nationalism with regards to increasing Western criticism.

 - **Government Surveillance in Public Areas**: This question asks if participants believe that the government has the right to surveil the populace in public areas. As this is one of the largest criticisms against the modern Chinese government, we can potentially see impacts of this variable with respect to life satisfaction for citizens. This variable is recorded on a scale of 1-4, with one being "Definitely should not have the right" and four being "Definitely should have the right"

 - **The Right for the Government to Monitor Emails**: This variable measures population sentiment for the governments ability to monitor private emails. While the last variable evaluated opinions on surveillance in public areas, this one angles more towards public sentiment on the collection of private information. This was also recorded on a scale of 1-4, with one being "Definitely should not have the right" and four being "Definitely should have the right".

 - **Should the Government Take More Responsibility to Ensure Everyone is Provided For?**: As the divide between communist and democratic ideals grow, this question will provide insight into the collectivist support among the general public in China. Although not a perfect capture of sentiment towards communism, this is the closest question that was able to be asked on the survey without running into political issues. This was recorded on a scale of 1-10, with one being the respondent completely agrees with the question and ten being the respondent completely disagrees.

 - **Age**: With the onset of social media, especially TikTok/Douyin, Chinese citizens are being exposed to more Western media than ever before. By measuring age, we can see if specific generations are more progressive than others. The World Values Survey limits the age of its participants to between 18 and 70.

## Data Analysis

Our investigation was conducted using the programming language R [@citeR], with the packages [@tidyverse], and [@dplyr]

Although each of the variables have a different scale, the summary statistics of the current dataset can be seen in @summary

```{r}
#| echo: false
#| label: summary
#| fig-cap: Summary Statistics for World Values Survey 2018
library(knitr)
library(kableExtra)
library(dplyr)
library(tidyr)

variables_of_interest <- c("National_Pride", "Happiness", "Government_Surveillance", 
                           "Email_Monitoring", "Information_Collection", 
                           "Government_Responsibility", "age")

# Calculate the summary statistics for the selected variables with rounding
summary_stats <- wvsdata %>%
  summarise(across(all_of(variables_of_interest), list(
    Mean = ~round(mean(.x, na.rm = TRUE), 2),
    SD = ~round(sd(.x, na.rm = TRUE), 2),
    Median = ~median(.x, na.rm = TRUE),
    Q1 = ~quantile(.x, probs = 0.25, na.rm = TRUE),
    Q3 = ~quantile(.x, probs = 0.75, na.rm = TRUE),
    Min = ~min(.x, na.rm = TRUE),
    Max = ~max(.x, na.rm = TRUE)
  ), .names = "{.col}_{.fn}"))

# Reshape the data frame to a long format and then to a wide format
summary_stats_long <- summary_stats %>%
  pivot_longer(cols = everything(), names_to = c("Variable", "Statistic"), names_pattern = "(.+)_(Mean|SD|Median|Q1|Q3|Min|Max)")

summary_stats_wide <- summary_stats_long %>%
  pivot_wider(names_from = Statistic, values_from = value)

# Create the summary table using kable for PDF output
summary_table <- kable(summary_stats_wide, format = "latex", booktabs = TRUE, 
                       caption = "Descriptive Statistics for Selected Variables") %>%
  row_spec(0, bold = TRUE)  # Make the header row bold

# Print the table
summary_table
```

\newpage

Initial observations of the summary statistics reveal that the mean happiness level is quite high, averaging to approximately 7.42 as opposed to the expected 5. Furthermore, we see that the median level of happiness is 8, significantly higher than expected. We also notice that national pride is very high, with a mean of 1.64. The interquartile range of 1-2 shows that vast majority of the populace are very proud of their status as Chinese citizens. The support for the various forms of government control seem middling, but it shows that the public is not vehemently opposed to these methods of surveillance.

We can also see the distribution for each of our variables in the following graphs:

```{r}
#| echo: false
#| label: distgraphs
#| fig-cap: Assorted Variable Distributions
#| warning: false
#| fig.height: 7

library(ggplot2)
library(gridExtra)

# Create a list to hold the ggplot objects
plot_list <- list()

plot_list[['National Pride']] <- ggplot(wvsdata, aes(x = National_Pride)) + 
      geom_histogram(bins = 5, fill = "blue") + 
      labs(title = "National Pride", x = "Responses (1-5)", y = "Count")

plot_list[['Happiness']] <- ggplot(wvsdata, aes(x = Happiness)) + 
      geom_histogram(bins = 10, fill = "red") + 
      labs(title = "Happiness", x = "Responses (1-10)", y = "Count")

plot_list[['Government Surveillance']] <- ggplot(wvsdata, aes(x = Government_Surveillance)) + 
      geom_histogram(bins = 4, fill = "green") + 
      labs(title = "Surveillance Support", x = "Responses (1-4)", y = "Count")

plot_list[['Email Monitoring']] <- ggplot(wvsdata, aes(x = Email_Monitoring)) + 
      geom_histogram(bins = 4, fill = "orange") + 
      labs(title = "Email Monitoring", x = "Responses (1-4)", y = "Count")

plot_list[['Information Collection']] <- ggplot(wvsdata, aes(x = Information_Collection)) + 
      geom_histogram(bins = 4, fill = "purple") + 
      labs(title = "Information Collection", x = "Responses (1-4)", y = "Count")

plot_list[['Government Responsibility']] <- ggplot(wvsdata, aes(x = Government_Responsibility)) + 
      geom_histogram(bins = 4, fill = "brown") + 
      labs(title = "Government Responsibility", x = "Responses (1-10)", y = "Count")

plot_list[['Age']] <- ggplot(wvsdata, aes(x = age)) + 
      geom_histogram(bins = 52, fill = "cyan") + 
      labs(title = "Age", x = "Age", y = "Count")

# Arrange the plots into a grid with 2 columns
do.call(grid.arrange, c(plot_list, ncol = 2))

```

From the distribution graphs shown in @distgraphs, we observe that barely any of the questions are normally distributed as we would expect for such a large sample. Although this could be attributed to the limited range of answers, we notice that even for questions with a larger range of responses like happiness and government responsibility, the data seems very skewed to one side.

Furthermore, the dataset provides information on how responses to question differ based off age. From this, we can depict how different age groups tend to respond to questions. For example, we expect the younger generation to be more progressive, leading to higher disapproval rates for government surveillance policies. 
```{r}
#| echo: false
#| warning: false
#| fig-cap: "Support for Government Surveillance Between Ages"
#| label: govsurvsup
wvsdata <- wvsdata %>%
  mutate(Age_Group = cut(age, 
                         breaks = c(18, 25, 35, 45, 55, 65, Inf),
                         labels = c("18-25", "26-35", "36-45", "46-55", "56-65", "66+"),
                         include.lowest = TRUE))
ggplot(wvsdata, aes(x = Age_Group, fill = as.factor(Government_Surveillance))) +
  geom_bar(position = "dodge") +
  labs(title = "Government Surveillance Support by Age Group",
       x = "Age Group",
       y = "Count",
       fill = "Gov. Surveillance\nSupport Level") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Surprisingly, we see that as age increases, a higher proportion of adults in that age group are opposed to government surveillance in public areas. As the question asks about government surveillance in public areas, we can potentially infer citizens may oppose government email/information supervision as those are more private. However, as seen in @compiled, we notice that the support for the collection of information for anybody in China is significantly higher than the other variables.

# Model

The potential of using the World Values Survey data to predict happiness is based on the idea that certain key variables, such as attitudes towards governance and societal structures, are able to predict an individual’s level of happiness. Our model will hopefully be able to show how and if specific perceptions on government surveillance acceptance, email monitoring, and information collection are indicative of broader societal satisfaction.

Before we develop our model, we have to assume that there is a relationship between our variables and happiness level. Research consistently indicates that the trust in, and perception of, governmental and societal systems significantly influences personal well-being (Helliwell & Putnam, 2004). We postulate that individuals’ responses to questions about governance and privacy are not merely reflective of their current state but are shaped by their broader socio-political environment and personal experiences. Therefore, a person's level of happiness is not only a function of their immediate circumstances but also a reflection of their interactions with the societal and political structures they inhabit (Bjørnskov, 2006).

To assess the validity and strength of these relationships, it is crucial to consider confounding factors that may be related to both the predictors and happiness. For instance, demographic variables such as age may influence both a person's perception of governance and their reported level of happiness. Older individuals may have different views on privacy and security, and simultaneously, their happiness levels might be affected by a host of age-related factors, making age a potential confounder that needs to be accounted for in our model.

Furthermore, cultural factors could moderate the relationship between governance attitudes and happiness. For example, in societies where collective well-being is emphasized, the acceptance of surveillance measures might correlate differently with happiness compared to societies that prioritize individual autonomy (Oishi, Diener, & Lucas, 2007).

## Model set-up

Define $y_i$ as the estimated level of happiness. Then $\beta_0$ would be the estimated level of happiness given that all other variables are zero, $\beta_i$ would be the respective effects on estimated levels of happiness for each of our variables. The full model form is shown below:

\begin{align} 
y_i &= \beta_0 + \beta_1 \cdot \text{Gov Surveillance}_i + \beta_2 \cdot \text{Email Monitoring}_i + \beta_3 \cdot \text{Info Collection}_i + \beta_4 \cdot \text{Age}_i + \beta_5 \cdot \text{National Pride}_i + \text{Government Responsibility}_i + \epsilon_i
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

In our study, we employ a multiple regression model to predict happiness levels using the World Values Survey data. Given that happiness is influenced by a diverse range of factors, a model that can handle multiple regressors is critical in understanding the relationship with variables such as government surveillance acceptance, email monitoring acceptance, information collection acceptance, and happiness. Furthermore, the model allows us to isolate the unique contributions of each predictor to happiness.

Our large sample size—approximately 3000 respondents—strengthens the model further. A robust sample size ensures that our parameter estimates are reliable and reduces the likelihood of statistical errors. It also increases the generalizability of our findings, ensuring that our conclusions are not just applicable to a narrow subset of the population but can be extended to China as a whole. Additionally, a larger dataset supports the complexity of our model, allowing us to include multiple predictors without the risk of overfitting, thereby maintaining the model’s integrity and robustness. The overall statistical significance of our test will be examined further later in this study.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

# Assuming your data frame is named 'wvsdata' and is properly formatted:
happiness_model <- stan_glm(
  Happiness ~ Government_Surveillance + Email_Monitoring + Information_Collection + National_Pride + age + Government_Responsibility,
  data = wvsdata,
  family = gaussian(),
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 2.5),
  prior_aux = exponential(1),
  chains = 4,
  iter = 2000,
  seed = 123456,
  refresh = 0
)

# Optionally, save your model for future use
saveRDS(happiness_model, file = here::here("models/happiness_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Regression Model Results for Predicting Happiness Based on Government Perceptions and Age"
#| warning: false

library(modelsummary)

modelsummary::modelsummary(
  list(
    "Happiness Model" = happiness_model
  ),
  statistic = "mad",  
  fmt = 2  
)
```
The regression analysis presented in Table 2 reveals an expected baseline happiness level of 7.60, as indicated by the model's intercept. This suggests a generally positive baseline level of happiness among respondents when all other variables are held constant. The coefficients for Government_Surveillance, Email_Monitoring, and Information_Collection are slightly negative, at -0.06, -0.01, and -0.01 respectively, suggesting a marginal decrease in happiness scores associated with increased acceptance of these governance measures. Notably, National_Pride shows a notably stronger negative association with happiness, with a coefficient of -0.50, indicating a significant decrease in happiness as national pride increases. In contrast, the age coefficient of 0.02 suggests a slight increase in happiness with age.

The model accounts for a modest 4.8% of the variance in happiness scores, as reflected by an R-squared value of 0.048, implying that other unexamined factors may play a more substantial role in influencing happiness. The adjusted R-squared value, at 0.043, indicates a minimal increase in explanatory power when accounting for the number of predictors. Furthermore, the Root Mean Square Error (RMSE) of 1.98 points to the model's prediction errors' standard deviation, signifying potential areas for model refinement. These results provide a statistical basis for the model's performance, emphasizing the nuanced challenge of predicting subjective well-being through perceived governance and age.
```{r}
#| echo: false
#| eval: true
#| warning: false
#| label: checks
#| fig-cap: "Happiness Model Checks"
library(rstanarm)
library(bayesplot)
library(ggplot2)

ppc_dens_overlay(y = wvsdata$Happiness, yrep = posterior_predict(happiness_model))

mcmc_trace(
  as.array(happiness_model),
  pars = c("(Intercept)", "Government_Surveillance", "Email_Monitoring", "Information_Collection", "National_Pride", "age", "Government_Responsibility")
)
```
The posterior predictive check, visualized by the ppc_dens_overlay plot, helps us evaluate the fit of our Bayesian model. By overlapping the observed happiness data with the simulated posterior predictive values, this plot illustrates how well our model reproduces the observed outcomes. The congruence between the values signifies that the model adequately captures the central tendency and variability of the actual happiness scores. Notably, if there are significant deviations it could indicate that the model may not fully account for the data's characteristics, prompting us to consider model refinements or additional predictors.

The trace plot provides a representation of the Markov Chain Monte Carlo (MCMC) sampling process, essential for evaluating the convergence of the chains. Each parameter's trace, represented by individual lines for each chain, should display a "mixing" behavior, converging to and fluctuating around a common value, without exhibiting trends or periodicity. Such patterns indicate that the chains have reached a stationary distribution, and the samples drawn are likely from the true posterior distribution. If the chains do not converge, this implies that the sampling process has not yet adequately captured the full behaviour of the true distribution, and further iterations or model adjustments may be required to ensure reliable inference.

# Discussion

## Model Findings {#sec-first-point}

As shown in our results section, we found that the initial baseline measure for happiness in China was quite high, at a predicted level of 7.60 given all other variables are at zero. We discover that our results disagree with Helliwell and Putnam's (2004) findings where belief in government policies are positively correlated with well-being. Our model suggests that an increase in support for any of the three policies correlates with a slight decrease in overall happiness level. However, we find that although national pride is negatively correlated with our measure of happiness, once we factor in that national pride is measured on a scale of 1-5 with 1 being the highest, we realize that national pride is the largest indicator of happiness out of our chosen variables. This could be because we are exclusively looking at a population of Chinese citizens. It is expected that residents and citizens that do not pride themselves in being Chinese are generally less happy while they are living there. Furthermore, we see a very slight positive coefficient for our age variable, suggesting that as Chinese citizens grow, they become more satisfied with their life. This could be potentially attributed to the stressful career and educational lifestyle of China. With a culture of overworking compounded with the pressure of the Gaokao, young citizens may experience lower levels of overall happiness compared to the older generation.

From our results, we see that even with growing discontentment towards China in the Western world, national pride and happiness levels seem to be unhindered and remain reasonably high. Yet, we also notice support for overreaching government policies with regards to surveillance and monitoring does not correlate with the high levels of national pride. Therefore, it is reasonable to conclude that although most Chinese citizens are very proud of their nationality, that does not necessarily correspond with support for the actions of the government.

## Weaknesses and next steps

With an R-squared value of 0.048, it seems that an incredibly small amount of variance is explained by our model. This is most likely due to omitted variable bias, where we neglected to include several other important factors when developing our regression model. Therefore, it is very likely that our chosen variables on support for government policies and/or national pride are not that significant in predicting overall happiness level. However, when considering the fact that the original questionnaire contained approximately 300 questions, it is to be expected that there would be a lot of unaccounted for variance in our data. Perhaps stronger expected indicators of overall happiness would consist marital status, annual income, and employment status. With regards to our model, we would likely get a more accurate regression by including more questions. However, due to the incredibly large amount of questions and responses, this could lead to overfitting. Although The R^2 value accounts partly for too many regressors, there is no feasible way to run a Bayesian regression model on all 300 questions. Therefore, future iterations of this study could look at combining several values into one. For example, support for government surveillance could be combined into one variable instead of three separate ones. Furthermore, questions that seem to have no impact on happiness level could also be ommitted by user discretion.

Future research may also consist of comparisons between different nations that partook in the World Values Survey. Specifically, comparisons for national pride and government support between communist and democratic countries may lead to interesting inferences on the societal beliefs for their respective nations. A heavier reliance on governmental structures in a communist society may lead to higher levels of national pride when compared to less reliant democratic nations.

\newpage

\appendix

# Appendix {-}

# Additional data details
```{r}
#| echo: false
#| warning: false
#| fig-cap: "Support for Surveillance, Email Monitoring, and Information Collection by Age Group"
#| label: compiled
#| fig.width: 6
library(ggplot2)
library(dplyr)

long_data <- wvsdata %>%
  select(Age_Group, Government_Surveillance, Email_Monitoring, Information_Collection, National_Pride, Government_Responsibility) %>%
  pivot_longer(cols = c(Government_Surveillance, Email_Monitoring, Information_Collection, National_Pride, Government_Responsibility), 
               names_to = "Variable", values_to = "Value")

# Plotting the responses for Government_Surveillance, Email_Monitoring, Information_Collection, and National Pride across different age groups
ggplot(long_data, aes(x = Age_Group, fill = as.factor(Value))) +
  geom_bar(position = "dodge") +
  facet_wrap(~ Variable, scales = "free_y") +  # Allows each facet to independently scale the y-axis
  scale_fill_brewer(palette = "Set2") +  # Using the "Set2" color palette for better aesthetics
  labs(title = "Support for Surveillance, Email Monitoring, Information Collection, Government Responsibility, and National Pride by Age Group",
       x = "Age Group",
       y = "Count",
       fill = "Response Level") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        strip.text = element_text(size = 8))
```

\newpage

# References

### 2024-04-23 scripts/01-download_data.R

@@ -1,0 +1,22 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from WSV
+# Author: Alexander Sun
+# Date: April 21st 2024
+# Contact: alexander.sun@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(opendatatoronto)
+library(tidyverse)
+library(arrow)
+# [...UPDATE THIS...]
+
+#### Download data ####
+raw_data <- read_csv("/Users/alexsun/Downloads/china_wellbeing/data/raw_data/wvsraw.csv")
+
+
+#### Save data ####
+write_csv(raw_data, "wvsraw.csv") 
+write_parquet(raw_data, "data/wvsraw.csv")
+         

### 2024-04-23 scripts/02-data_cleaning.R

@@ -1,0 +1,37 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from WSV
+# Author: Alexander Sun
+# Date: April 21st 2024
+# Contact: alexander.sun@mail.utoronto.ca
+# License: MIT
+
+#### Workspace setup ####
+library(tidyverse)
+library(dplyr)
+
+#### Clean data ####
+raw_data <- read_csv("/Users/alexsun/Downloads/china_wellbeing/data/raw_data/wvsraw.csv")
+cleaned_data <- raw_data %>%
+  filter(B_COUNTRY_ALPHA == "CHN") %>%
+  select(year = A_YEAR, national_pride = Q254, happiness = Q49, 
+         surveillance_right = Q196, email_monitoring_right = Q197, 
+         info_collection_right = Q198, government_responsibility = Q108, age = Q262) %>%
+  filter(!if_any(c(national_pride, happiness, surveillance_right, 
+                   email_monitoring_right, info_collection_right, 
+                   government_responsibility, age), ~ . %in% c(-1, -2)))
+
+
+cleaned_data <- cleaned_data %>%
+  rename(
+    Email_Monitoring = email_monitoring_right,
+    Information_Collection = info_collection_right,
+    Government_Surveillance = surveillance_right,
+    National_Pride = national_pride,
+    Happiness = happiness,
+    Government_Responsibility = government_responsibility,
+    Year = year
+  )
+
+#### Save data ####
+write_parquet(cleaned_data, "data/analysis_data/analysis_data2018.parquet")
+

### 2024-04-23 paper/paper.qmd
i can't fix it i give up

@@
 ---
-title: "Pursuit of Happiness"
-subtitle: "The impact of growing Western criticism on Chinese Wellbeing"
+title: "Pursuit of Happiness: The impact of growing Western criticism on Chinese Wellbeing"
 author: 
   - Alexander Sun
-thanks: "Code and data are available at: https://github.com/alexandersunliang/china_wellbeing.git"
+thanks: "Code and data are available at: https://github.com/alexandersunliang/china_wellbeing2bugfix.git"
 date: today
@@
 format: pdf
+toc: true
 number-sections: true
@@
 
-# Introduction
+# Introduction {#sec-intro}
 
@@
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
-
-The remainder of this paper is structured as follows. @sec-data....
+The remainder of the paper is structured as follows: following in the introduction in [@sec-intro], [@sec-data] provides an overview of our dataset, variables, and a quick analysis of the data, [@sec-model] discusses the model we chose for our regression, [@sec-results] depicts the calculated values along with any important measurements, and [@sec-discussion] discusses the implications of our results while also suggesting avenues for future research.
 
@@
 
-## Data Source
+## Data Source and Measurement
 
@@
 Each wave of the survey is slightly different, so the wording of some questions and answers may vary.
+Although the sample for China was chosen through random sampling, survey guidelines dictated that there would be no replacement for non-responses.
+Therefore, missing data would have to be parsed out.
 
@@
 
-Although each of the variables have a different scale, the summary statistics of the current dataset can be seen in @summary
+Although each of the variables have a different scale, the summary statistics of the current dataset can be seen in @fig-summary
 
@@
 #| echo: false
-#| label: summary
-#| fig-cap: Summary Statistics for World Values Survey 2018
+#| label: fig-summary
+#| fig-cap: Summary Statistics for World Values Survey
 library(knitr)
@@
 
-# Calculate the summary statistics for the selected variables with rounding
 summary_stats <- wvsdata %>%
@@
 
-# Reshape the data frame to a long format and then to a wide format
 summary_stats_long <- summary_stats %>%
@@
 
-# Create the summary table using kable for PDF output
 summary_table <- kable(summary_stats_wide, format = "latex", booktabs = TRUE, 
                        caption = "Descriptive Statistics for Selected Variables") %>%
-  row_spec(0, bold = TRUE)  # Make the header row bold
+  row_spec(0, bold = TRUE)
 
-# Print the table
 summary_table
 ```
-
-\newpage
 
@@
 
-We can also see the distribution for each of our variables in the following graphs:
+We can also see the distribution for each of our variables in @fig-distgraphs:
 
@@
 #| echo: false
-#| label: distgraphs
+#| label: fig-distgraphs
 #| fig-cap: Assorted Variable Distributions
@@
 
-From the distribution graphs shown in @distgraphs, we observe that barely any of the questions are normally distributed as we would expect for such a large sample.
+From the distribution graphs shown in @fig-distgraphs, we observe that barely any of the questions are normally distributed as we would expect for such a large sample.
 Although this could be attributed to the limited range of answers, we notice that even for questions with a larger range of responses like happiness and government responsibility, the data seems very skewed to one side.
@@
 For example, we expect the younger generation to be more progressive, leading to higher disapproval rates for government surveillance policies.
+Information on age distributions on support for government surveillance is shown in @fig-govsurvsup.
 ```{r}
@@
 #| fig-cap: "Support for Government Surveillance Between Ages"
-#| label: govsurvsup
+#| label: fig-govsurvsup
 wvsdata <- wvsdata %>%
@@
 As the question asks about government surveillance in public areas, we can potentially infer citizens may oppose government email/information supervision as those are more private.
-However, as seen in @compiled, we notice that the support for the collection of information for anybody in China is significantly higher than the other variables.
+However, as seen in @fig-compiled, we notice that the support for the collection of information for anybody in China is significantly higher than the other variables.
 
-# Model
+# Model {@sec-model}
 
@@
 For example, in societies where collective well-being is emphasized, the acceptance of surveillance measures might correlate differently with happiness compared to societies that prioritize individual autonomy (Oishi, Diener, & Lucas, 2007).
+We expect that the effects for the government policies and age to be positive, while national pride is negative.
 
@@
 
-### Model justification
+## Model justification
 
@@
 
-# Results
+# Results {@sec-results}
 
@@
 
-library(rstanarm)
-
-# Assuming your data frame is named 'wvsdata' and is properly formatted:
-happiness_model <- stan_glm(
-  Happiness ~ Government_Surveillance + Email_Monitoring + Information_Collection + National_Pride + age + Government_Responsibility,
-  data = wvsdata,
-  family = gaussian(),
-  prior = normal(0, 2.5),
-  prior_intercept = normal(0, 2.5),
-  prior_aux = exponential(1),
-  chains = 4,
-  iter = 2000,
-  seed = 123456,
-  refresh = 0
-)
-
-# Optionally, save your model for future use
-saveRDS(happiness_model, file = here::here("models/happiness_model.rds"))
+happiness_model <- readRDS(here(file = "models/happiness_model.rds"))
 ```
@@
 library(modelsummary)
-
 modelsummary::modelsummary(
-  list(
-    "Happiness Model" = happiness_model
-  ),
+  happiness_model,
   statistic = "mad",  
@@
 ```
-The regression analysis presented in Table 2 reveals an expected baseline happiness level of 7.60, as indicated by the model's intercept.
+The regression analysis presented in @tbl-modelresults reveals an expected baseline happiness level of 7.60, as indicated by the model's intercept.
 This suggests a generally positive baseline level of happiness among respondents when all other variables are held constant.
-The coefficients for Government_Surveillance, Email_Monitoring, and Information_Collection are slightly negative, at -0.06, -0.01, and -0.01 respectively, suggesting a marginal decrease in happiness scores associated with increased acceptance of these governance measures.
-Notably, National_Pride shows a notably stronger negative association with happiness, with a coefficient of -0.50, indicating a significant decrease in happiness as national pride increases.
+The coefficients for the support for government surveillance, email monitoring, and information collection are slightly negative, at -0.06, -0.01, and -0.01 respectively, suggesting a marginal decrease in happiness scores associated with increased acceptance of these governance measures.
+Notably, national pride shows a stronger negative association with happiness, with a coefficient of -0.50, indicating a significant decrease in happiness as national pride increases.
 In contrast, the age coefficient of 0.02 suggests a slight increase in happiness with age.
@@
 #| warning: false
-#| label: checks
+#| label: fig-checks
 #| fig-cap: "Happiness Model Checks"
@@
 ```
-The posterior predictive check, visualized by the ppc_dens_overlay plot, helps us evaluate the fit of our Bayesian model.
+The posterior predictive check, visualized by @fig-checks, helps us evaluate the fit of our Bayesian model.
 By overlapping the observed happiness data with the simulated posterior predictive values, this plot illustrates how well our model reproduces the observed outcomes.
@@
 
-# Discussion
+# Discussion {@sec-discussion}
 
@@
 
-As shown in our results section, we found that the initial baseline measure for happiness in China was quite high, at a predicted level of 7.60 given all other variables are at zero.
+As shown in our @sec-results section, we found that the initial baseline measure for happiness in China was quite high, at a predicted level of 7.60 given all other variables are at zero.
 We discover that our results disagree with Helliwell and Putnam's (2004) findings where belief in government policies are positively correlated with well-being.
@@
 However, due to the incredibly large amount of questions and responses, this could lead to overfitting.
-Although The R^2 value accounts partly for too many regressors, there is no feasible way to run a Bayesian regression model on all 300 questions.
+Although the adjusted R-squared value accounts partly for too many regressors, there is no feasible way to run a Bayesian regression model on all 300 questions.
 Therefore, future iterations of this study could look at combining several values into one.
@@
 
-# Appendix {-}
+# Appendix {@sec-appendix}
 
-# Additional data details
 ```{r}
@@
 #| fig-cap: "Support for Surveillance, Email Monitoring, and Information Collection by Age Group"
-#| label: compiled
+#| label: fig-compiled
 #| fig.width: 6

### 2024-04-23 paper/paper.tex
i can't fix it i give up

--- 2024-04-23 paper/paper.qmd
@@
----
-title: "Pursuit of Happiness: The impact of growing Western criticism on Chinese Wellbeing"
-author: 
-  - Alexander Sun
-thanks: "Code and data are available at: https://github.com/alexandersunliang/china_wellbeing2bugfix.git"
-date: today
-date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
-format: pdf
-toc: true
-number-sections: true
-bibliography: references.bib
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
 
-```{r}
-#| include: false
-#| warning: false
-#| message: false
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else  
+    % xetex/luatex font selection
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-library(tidyverse)
-library(arrow)
-library(here)
-library(modelsummary)
-library(knitr)
-library(kableExtra)
-wvsdata <- read_parquet(here("data/analysis_data/analysis_data2018.parquet"))
-```
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-# Introduction {#sec-intro}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\usepackage{siunitx}
 
-Since the early 1990s, China's economy has grown significantly, with an average annual GDP growth rate of around 10%.
-The 1990s market reforms aimed to control capitalism, showing that socialism could harness capitalist growth to increase national power.
-Today, China is a global economic leader, second only to the US in GDP; however, it is essential to assess how these changes affect societal well-being.
-Studies present mixed views on the effects of socialism and democracy.
-Cheung and Leung (2007) found that collectivism significantly impacts the well-being of the Chinese, whereas Hofstede (1980) observed that individualism encourages economic growth.
-Moore (2005) argued that the freedoms introduced in the 1980s led the Chinese towards a strong form of individualism, which starkly contrasts with the collectivist approach of the Cultural Revolution.
-Steele and Lynch examined whether individualist or collectivist traits prevail in modern China and their impact on subjective well-being (SWB).
-They focused on how these orientations predict SWB and if their influence has shifted as China transitioned towards a market economy.
+  \newcolumntype{d}{S[
+    input-open-uncertainty=,
+    input-close-uncertainty=,
+    parse-numbers = false,
+    table-align-text-pre=false,
+    table-align-text-post=false
+  ]}
 
-While Steele and Lynch researched the impacts of the reform, this paper will attempt to reframe their ideas with a focus on the impacts of COVID-19.
-This study will replicate and extend Steele and Lynch’s previous research by examining the prevailing sentiments—individualist versus collectivist—in China post-COVID-19 in 2022 and their implications for SWB.
-We analyze whether and how the relationship between these cultural orientations and well-being has evolved in the context of China's continued economic and social transformations.
+\KOMAoption{captions}{tableheading}
+\makeatletter
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
+\makeatother
+\makeatletter
+\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\makeatother
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Pursuit of Happiness: The impact of growing Western criticism on Chinese Wellbeing},
+  pdfauthor={Alexander Sun},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
-In this project, the estimand will be the difference in happiness level between each participant based on information like national pride, government support, and age.
+\title{Pursuit of Happiness: The impact of growing Western criticism on
+Chinese Wellbeing\thanks{Code and data are available at:
+https://github.com/alexandersunliang/china\_wellbeing2bugfix.git}}
+\author{Alexander Sun}
+\date{April 22, 2024}
 
-The remainder of the paper is structured as follows: following in the introduction in [@sec-intro], [@sec-data] provides an overview of our dataset, variables, and a quick analysis of the data, [@sec-model] discusses the model we chose for our regression, [@sec-results] depicts the calculated values along with any important measurements, and [@sec-discussion] discusses the implications of our results while also suggesting avenues for future research.
+\begin{document}
+\maketitle
+\begin{abstract}
+First sentence. Second sentence. Third sentence. Fourth sentence.
+\end{abstract}
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners, enhanced, interior hidden, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi
 
-# Data {#sec-data}
+\renewcommand*\contentsname{Table of contents}
+{
+\hypersetup{linkcolor=}
+\setcounter{tocdepth}{3}
+\tableofcontents
+}
+\hypertarget{sec-intro}{%
+\section{Introduction}\label{sec-intro}}
 
-## Data Source and Measurement
+Since the early 1990s, China's economy has grown significantly, with an
+average annual GDP growth rate of around 10\%. The 1990s market reforms
+aimed to control capitalism, showing that socialism could harness
+capitalist growth to increase national power. Today, China is a global
+economic leader, second only to the US in GDP; however, it is essential
+to assess how these changes affect societal well-being. Studies present
+mixed views on the effects of socialism and democracy. Cheung and Leung
+(2007) found that collectivism significantly impacts the well-being of
+the Chinese, whereas Hofstede (1980) observed that individualism
+encourages economic growth. Moore (2005) argued that the freedoms
+introduced in the 1980s led the Chinese towards a strong form of
+individualism, which starkly contrasts with the collectivist approach of
+the Cultural Revolution. Steele and Lynch examined whether individualist
+or collectivist traits prevail in modern China and their impact on
+subjective well-being (SWB). They focused on how these orientations
+predict SWB and if their influence has shifted as China transitioned
+towards a market economy.
 
-To replicate the paper by Steele and Lynch, we obtained our data from the World Values Survey.
-While Steele and Lynch used time series data from three surveys (1990, 2001, 2007), we aim to look at more recent trends so we will include the World Values Survey data obtained from their 2018 wave.
-To be included into the survey dataset, countries must meet a minimum of 1200 entries.
-Since the survey is global, general guidelines are provided to the teams that are responsible for each country, but slight alterations in sampling method were permitted.
-The most common method of data collection consisted of face-to-face interviews with respondents at their home, and the answers were recorded on a paper questionnaire for later processing.
-For China, participants were chosen through probability sampling.
-The initial dataset contained 94278 responses and 606 variables, but after filtering for responses from China and removing non-responses, we are left with 3036 observations.
-Each wave of the survey is slightly different, so the wording of some questions and answers may vary.
-Although the sample for China was chosen through random sampling, survey guidelines dictated that there would be no replacement for non-responses.
-Therefore, missing data would have to be parsed out.
+While Steele and Lynch researched the impacts of the reform, this paper
+will attempt to reframe their ideas with a focus on the impacts of
+COVID-19. This study will replicate and extend Steele and Lynch's
+previous research by examining the prevailing sentiments---individualist
+versus collectivist---in China post-COVID-19 in 2022 and their
+implications for SWB. We analyze whether and how the relationship
+between these cultural orientations and well-being has evolved in the
+context of China's continued economic and social transformations.
 
-## Variables
+In this project, the estimand will be the difference in happiness level
+between each participant based on information like national pride,
+government support, and age.
 
-The original questionnaire was composed of approximately 300 questions, but for the purposes of our study we will focus on the following:
+The remainder of the paper is structured as follows: following in the
+introduction in Section~\ref{sec-intro}, Section~\ref{sec-data} provides
+an overview of our dataset, variables, and a quick analysis of the data,
+\textbf{?@sec-model} discusses the model we chose for our regression,
+\textbf{?@sec-results} depicts the calculated values along with any
+important measurements, and \textbf{?@sec-discussion} discusses the
+implications of our results while also suggesting avenues for future
+research.
 
- - **Happiness**: Our dependent variable was measured as "life satisfaction" in the questionnaire.
-Participants responded with how happy they were with their current lifestyle on a scale of 1-10 with 1 being "completely dissatisfied" and 10 being "completely satisfied".
-We will later conduct a model to estimate this value based off our other regressors.
+\hypertarget{sec-data}{%
+\section{Data}\label{sec-data}}
 
- - **National Pride**: Respondents were asked about their national pride with the question, "How proud are you to be Chinese?" We believe that this is especially important as it allows us to see temporal trends in nationalism with regards to increasing Western criticism.
+\hypertarget{data-source-and-measurement}{%
+\subsection{Data Source and
+Measurement}\label{data-source-and-measurement}}
 
- - **Government Surveillance in Public Areas**: This question asks if participants believe that the government has the right to surveil the populace in public areas.
-As this is one of the largest criticisms against the modern Chinese government, we can potentially see impacts of this variable with respect to life satisfaction for citizens.
-This variable is recorded on a scale of 1-4, with one being "Definitely should not have the right" and four being "Definitely should have the right"
+To replicate the paper by Steele and Lynch, we obtained our data from
+the World Values Survey. While Steele and Lynch used time series data
+from three surveys (1990, 2001, 2007), we aim to look at more recent
+trends so we will include the World Values Survey data obtained from
+their 2018 wave. To be included into the survey dataset, countries must
+meet a minimum of 1200 entries. Since the survey is global, general
+guidelines are provided to the teams that are responsible for each
+country, but slight alterations in sampling method were permitted. The
+most common method of data collection consisted of face-to-face
+interviews with respondents at their home, and the answers were recorded
+on a paper questionnaire for later processing. For China, participants
+were chosen through probability sampling. The initial dataset contained
+94278 responses and 606 variables, but after filtering for responses
+from China and removing non-responses, we are left with 3036
+observations. Each wave of the survey is slightly different, so the
+wording of some questions and answers may vary. Although the sample for
+China was chosen through random sampling, survey guidelines dictated
+that there would be no replacement for non-responses. Therefore, missing
+data would have to be parsed out.
 
- - **The Right for the Government to Monitor Emails**: This variable measures population sentiment for the governments ability to monitor private emails.
-While the last variable evaluated opinions on surveillance in public areas, this one angles more towards public sentiment on the collection of private information.
-This was also recorded on a scale of 1-4, with one being "Definitely should not have the right" and four being "Definitely should have the right".
+\hypertarget{variables}{%
+\subsection{Variables}\label{variables}}
 
- - **Should the Government Take More Responsibility to Ensure Everyone is Provided For?**: As the divide between communist and democratic ideals grow, this question will provide insight into the collectivist support among the general public in China.
-Although not a perfect capture of sentiment towards communism, this is the closest question that was able to be asked on the survey without running into political issues.
-This was recorded on a scale of 1-10, with one being the respondent completely agrees with the question and ten being the respondent completely disagrees.
+The original questionnaire was composed of approximately 300 questions,
+but for the purposes of our study we will focus on the following:
 
- - **Age**: With the onset of social media, especially TikTok/Douyin, Chinese citizens are being exposed to more Western media than ever before.
-By measuring age, we can see if specific generations are more progressive than others.
-The World Values Survey limits the age of its participants to between 18 and 70.
+\begin{itemize}
+\item
+  \textbf{Happiness}: Our dependent variable was measured as ``life
+  satisfaction'' in the questionnaire. Participants responded with how
+  happy they were with their current lifestyle on a scale of 1-10 with 1
+  being ``completely dissatisfied'' and 10 being ``completely
+  satisfied''. We will later conduct a model to estimate this value
+  based off our other regressors.
+\item
+  \textbf{National Pride}: Respondents were asked about their national
+  pride with the question, ``How proud are you to be Chinese?'' We
+  believe that this is especially important as it allows us to see
+  temporal trends in nationalism with regards to increasing Western
+  criticism.
+\item
+  \textbf{Government Surveillance in Public Areas}: This question asks
+  if participants believe that the government has the right to surveil
+  the populace in public areas. As this is one of the largest criticisms
+  against the modern Chinese government, we can potentially see impacts
+  of this variable with respect to life satisfaction for citizens. This
+  variable is recorded on a scale of 1-4, with one being ``Definitely
+  should not have the right'' and four being ``Definitely should have
+  the right''
+\item
+  \textbf{The Right for the Government to Monitor Emails}: This variable
+  measures population sentiment for the governments ability to monitor
+  private emails. While the last variable evaluated opinions on
+  surveillance in public areas, this one angles more towards public
+  sentiment on the collection of private information. This was also
+  recorded on a scale of 1-4, with one being ``Definitely should not
+  have the right'' and four being ``Definitely should have the right''.
+\item
+  \textbf{Should the Government Take More Responsibility to Ensure
+  Everyone is Provided For?}: As the divide between communist and
+  democratic ideals grow, this question will provide insight into the
+  collectivist support among the general public in China. Although not a
+  perfect capture of sentiment towards communism, this is the closest
+  question that was able to be asked on the survey without running into
+  political issues. This was recorded on a scale of 1-10, with one being
+  the respondent completely agrees with the question and ten being the
+  respondent completely disagrees.
+\item
+  \textbf{Age}: With the onset of social media, especially
+  TikTok/Douyin, Chinese citizens are being exposed to more Western
+  media than ever before. By measuring age, we can see if specific
+  generations are more progressive than others. The World Values Survey
+  limits the age of its participants to between 18 and 70.
+\end{itemize}
 
-## Data Analysis
+\hypertarget{data-analysis}{%
+\subsection{Data Analysis}\label{data-analysis}}
 
-Our investigation was conducted using the programming language R [@citeR], with the packages [@tidyverse], and [@dplyr]
+Our investigation was conducted using the programming language R (R Core
+Team 2023), with the packages (\textbf{tidyverse?}), and
+(\textbf{dplyr?})
 
-Although each of the variables have a different scale, the summary statistics of the current dataset can be seen in @fig-summary
+Although each of the variables have a different scale, the summary
+statistics of the current dataset can be seen in
+Figure~\ref{fig-summary}
 
-```{r}
-#| echo: false
-#| label: fig-summary
-#| fig-cap: Summary Statistics for World Values Survey
-library(knitr)
-library(kableExtra)
-library(dplyr)
-library(tidyr)
+\begin{figure}
 
-variables_of_interest <- c("National_Pride", "Happiness", "Government_Surveillance", 
-                           "Email_Monitoring", "Information_Collection", 
-                           "Government_Responsibility", "age")
+{\centering
 
-summary_stats <- wvsdata %>%
-  summarise(across(all_of(variables_of_interest), list(
-    Mean = ~round(mean(.x, na.rm = TRUE), 2),
-    SD = ~round(sd(.x, na.rm = TRUE), 2),
-    Median = ~median(.x, na.rm = TRUE),
-    Q1 = ~quantile(.x, probs = 0.25, na.rm = TRUE),
-    Q3 = ~quantile(.x, probs = 0.75, na.rm = TRUE),
-    Min = ~min(.x, na.rm = TRUE),
-    Max = ~max(.x, na.rm = TRUE)
-  ), .names = "{.col}_{.fn}"))
+\hypertarget{fig-summary-1}{}
+\begin{table}
 
-summary_stats_long <- summary_stats %>%
-  pivot_longer(cols = everything(), names_to = c("Variable", "Statistic"), names_pattern = "(.+)_(Mean|SD|Median|Q1|Q3|Min|Max)")
+\caption{Descriptive Statistics for Selected Variables}
+\centering
+\begin{tabular}[t]{lrrrrrrr}
+\toprule
+\textbf{Variable} & \textbf{Mean} & \textbf{SD} & \textbf{Median} & \textbf{Q1} & \textbf{Q3} & \textbf{Min} & \textbf{Max}\\
+\midrule
+National\_Pride & 1.64 & 0.64 & 2 & 1 & 2 & 1 & 5\\
+Happiness & 7.42 & 2.02 & 8 & 6 & 9 & 1 & 10\\
+Government\_Surveillance & 1.82 & 0.89 & 2 & 1 & 2 & 1 & 4\\
+Email\_Monitoring & 2.30 & 0.98 & 2 & 2 & 3 & 1 & 4\\
+Information\_Collection & 2.48 & 1.04 & 2 & 2 & 3 & 1 & 4\\
+\addlinespace
+Government\_Responsibility & 5.22 & 2.82 & 5 & 3 & 8 & 1 & 10\\
+age & 44.46 & 14.48 & 45 & 32 & 56 & 18 & 70\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-summary_stats_wide <- summary_stats_long %>%
-  pivot_wider(names_from = Statistic, values_from = value)
+}
 
-summary_table <- kable(summary_stats_wide, format = "latex", booktabs = TRUE, 
-                       caption = "Descriptive Statistics for Selected Variables") %>%
-  row_spec(0, bold = TRUE)
+\caption{\label{fig-summary}Summary Statistics for World Values Survey}
 
-summary_table
-```
+\end{figure}
 
-Initial observations of the summary statistics reveal that the mean happiness level is quite high, averaging to approximately 7.42 as opposed to the expected 5.
-Furthermore, we see that the median level of happiness is 8, significantly higher than expected.
-We also notice that national pride is very high, with a mean of 1.64.
-The interquartile range of 1-2 shows that vast majority of the populace are very proud of their status as Chinese citizens.
-The support for the various forms of government control seem middling, but it shows that the public is not vehemently opposed to these methods of surveillance.
+Initial observations of the summary statistics reveal that the mean
+happiness level is quite high, averaging to approximately 7.42 as
+opposed to the expected 5. Furthermore, we see that the median level of
+happiness is 8, significantly higher than expected. We also notice that
+national pride is very high, with a mean of 1.64. The interquartile
+range of 1-2 shows that vast majority of the populace are very proud of
+their status as Chinese citizens. The support for the various forms of
+government control seem middling, but it shows that the public is not
+vehemently opposed to these methods of surveillance.
 
-We can also see the distribution for each of our variables in @fig-distgraphs:
+We can also see the distribution for each of our variables in
+Figure~\ref{fig-distgraphs}:
 
-```{r}
-#| echo: false
-#| label: fig-distgraphs
-#| fig-cap: Assorted Variable Distributions
-#| warning: false
-#| fig.height: 7
+\begin{figure}
 
-library(ggplot2)
-library(gridExtra)
+{\centering \includegraphics{paper_files/figure-pdf/fig-distgraphs-1.pdf}
 
-# Create a list to hold the ggplot objects
-plot_list <- list()
+}
 
-plot_list[['National Pride']] <- ggplot(wvsdata, aes(x = National_Pride)) + 
-      geom_histogram(bins = 5, fill = "blue") + 
-      labs(title = "National Pride", x = "Responses (1-5)", y = "Count")
+\caption{\label{fig-distgraphs}Assorted Variable Distributions}
 
-plot_list[['Happiness']] <- ggplot(wvsdata, aes(x = Happiness)) + 
-      geom_histogram(bins = 10, fill = "red") + 
-      labs(title = "Happiness", x = "Responses (1-10)", y = "Count")
+\end{figure}
 
-plot_list[['Government Surveillance']] <- ggplot(wvsdata, aes(x = Government_Surveillance)) + 
-      geom_histogram(bins = 4, fill = "green") + 
-      labs(title = "Surveillance Support", x = "Responses (1-4)", y = "Count")
+From the distribution graphs shown in Figure~\ref{fig-distgraphs}, we
+observe that barely any of the questions are normally distributed as we
+would expect for such a large sample. Although this could be attributed
+to the limited range of answers, we notice that even for questions with
+a larger range of responses like happiness and government
+responsibility, the data seems very skewed to one side.
 
-plot_list[['Email Monitoring']] <- ggplot(wvsdata, aes(x = Email_Monitoring)) + 
-      geom_histogram(bins = 4, fill = "orange") + 
-      labs(title = "Email Monitoring", x = "Responses (1-4)", y = "Count")
+Furthermore, the dataset provides information on how responses to
+question differ based off age. From this, we can depict how different
+age groups tend to respond to questions. For example, we expect the
+younger generation to be more progressive, leading to higher disapproval
+rates for government surveillance policies. Information on age
+distributions on support for government surveillance is shown in
+Figure~\ref{fig-govsurvsup}.
 
-plot_list[['Information Collection']] <- ggplot(wvsdata, aes(x = Information_Collection)) + 
-      geom_histogram(bins = 4, fill = "purple") + 
-      labs(title = "Information Collection", x = "Responses (1-4)", y = "Count")
+\begin{figure}
 
-plot_list[['Government Responsibility']] <- ggplot(wvsdata, aes(x = Government_Responsibility)) + 
-      geom_histogram(bins = 4, fill = "brown") + 
-      labs(title = "Government Responsibility", x = "Responses (1-10)", y = "Count")
+{\centering \includegraphics{paper_files/figure-pdf/fig-govsurvsup-1.pdf}
 
-plot_list[['Age']] <- ggplot(wvsdata, aes(x = age)) + 
-      geom_histogram(bins = 52, fill = "cyan") + 
-      labs(title = "Age", x = "Age", y = "Count")
+}
 
-# Arrange the plots into a grid with 2 columns
-do.call(grid.arrange, c(plot_list, ncol = 2))
+\caption{\label{fig-govsurvsup}Support for Government Surveillance
+Between Ages}
 
-```
+\end{figure}
 
-From the distribution graphs shown in @fig-distgraphs, we observe that barely any of the questions are normally distributed as we would expect for such a large sample.
-Although this could be attributed to the limited range of answers, we notice that even for questions with a larger range of responses like happiness and government responsibility, the data seems very skewed to one side.
+Surprisingly, we see that as age increases, a higher proportion of
+adults in that age group are opposed to government surveillance in
+public areas. As the question asks about government surveillance in
+public areas, we can potentially infer citizens may oppose government
+email/information supervision as those are more private. However, as
+seen in Figure~\ref{fig-compiled}, we notice that the support for the
+collection of information for anybody in China is significantly higher
+than the other variables.
 
-Furthermore, the dataset provides information on how responses to question differ based off age.
-From this, we can depict how different age groups tend to respond to questions.
-For example, we expect the younger generation to be more progressive, leading to higher disapproval rates for government surveillance policies.
-Information on age distributions on support for government surveillance is shown in @fig-govsurvsup.
-```{r}
-#| echo: false
-#| warning: false
-#| fig-cap: "Support for Government Surveillance Between Ages"
-#| label: fig-govsurvsup
-wvsdata <- wvsdata %>%
-  mutate(Age_Group = cut(age, 
-                         breaks = c(18, 25, 35, 45, 55, 65, Inf),
-                         labels = c("18-25", "26-35", "36-45", "46-55", "56-65", "66+"),
-                         include.lowest = TRUE))
-ggplot(wvsdata, aes(x = Age_Group, fill = as.factor(Government_Surveillance))) +
-  geom_bar(position = "dodge") +
-  labs(title = "Government Surveillance Support by Age Group",
-       x = "Age Group",
-       y = "Count",
-       fill = "Gov. Surveillance\nSupport Level") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-Surprisingly, we see that as age increases, a higher proportion of adults in that age group are opposed to government surveillance in public areas.
-As the question asks about government surveillance in public areas, we can potentially infer citizens may oppose government email/information supervision as those are more private.
-However, as seen in @fig-compiled, we notice that the support for the collection of information for anybody in China is significantly higher than the other variables.
+\hypertarget{model-sec-model}{%
+\section{\texorpdfstring{Model
+\{\textbf{?@sec-model}\}}{Model \{?@sec-model\}}}\label{model-sec-model}}
 
-# Model {@sec-model}
+The potential of using the World Values Survey data to predict happiness
+is based on the idea that certain key variables, such as attitudes
+towards governance and societal structures, are able to predict an
+individual's level of happiness. Our model will hopefully be able to
+show how and if specific perceptions on government surveillance
+acceptance, email monitoring, and information collection are indicative
+of broader societal satisfaction.
 
-The potential of using the World Values Survey data to predict happiness is based on the idea that certain key variables, such as attitudes towards governance and societal structures, are able to predict an individual’s level of happiness.
-Our model will hopefully be able to show how and if specific perceptions on government surveillance acceptance, email monitoring, and information collection are indicative of broader societal satisfaction.
+Before we develop our model, we have to assume that there is a
+relationship between our variables and happiness level. Research
+consistently indicates that the trust in, and perception of,
+governmental and societal systems significantly influences personal
+well-being (Helliwell \& Putnam, 2004). We postulate that individuals'
+responses to questions about governance and privacy are not merely
+reflective of their current state but are shaped by their broader
+socio-political environment and personal experiences. Therefore, a
+person's level of happiness is not only a function of their immediate
+circumstances but also a reflection of their interactions with the
+societal and political structures they inhabit (Bjørnskov, 2006).
 
-Before we develop our model, we have to assume that there is a relationship between our variables and happiness level.
-Research consistently indicates that the trust in, and perception of, governmental and societal systems significantly influences personal well-being (Helliwell & Putnam, 2004).
-We postulate that individuals’ responses to questions about governance and privacy are not merely reflective of their current state but are shaped by their broader socio-political environment and personal experiences.
-Therefore, a person's level of happiness is not only a function of their immediate circumstances but also a reflection of their interactions with the societal and political structures they inhabit (Bjørnskov, 2006).
+To assess the validity and strength of these relationships, it is
+crucial to consider confounding factors that may be related to both the
+predictors and happiness. For instance, demographic variables such as
+age may influence both a person's perception of governance and their
+reported level of happiness. Older individuals may have different views
+on privacy and security, and simultaneously, their happiness levels
+might be affected by a host of age-related factors, making age a
+potential confounder that needs to be accounted for in our model.
 
-To assess the validity and strength of these relationships, it is crucial to consider confounding factors that may be related to both the predictors and happiness.
-For instance, demographic variables such as age may influence both a person's perception of governance and their reported level of happiness.
-Older individuals may have different views on privacy and security, and simultaneously, their happiness levels might be affected by a host of age-related factors, making age a potential confounder that needs to be accounted for in our model.
+Furthermore, cultural factors could moderate the relationship between
+governance attitudes and happiness. For example, in societies where
+collective well-being is emphasized, the acceptance of surveillance
+measures might correlate differently with happiness compared to
+societies that prioritize individual autonomy (Oishi, Diener, \& Lucas,
+2007). We expect that the effects for the government policies and age to
+be positive, while national pride is negative.
 
-Furthermore, cultural factors could moderate the relationship between governance attitudes and happiness.
-For example, in societies where collective well-being is emphasized, the acceptance of surveillance measures might correlate differently with happiness compared to societies that prioritize individual autonomy (Oishi, Diener, & Lucas, 2007).
-We expect that the effects for the government policies and age to be positive, while national pride is negative.
+\hypertarget{model-set-up}{%
+\subsection{Model set-up}\label{model-set-up}}
 
-## Model set-up
-
-Define $y_i$ as the estimated level of happiness.
-Then $\beta_0$ would be the estimated level of happiness given that all other variables are zero, $\beta_i$ would be the respective effects on estimated levels of happiness for each of our variables.
-The full model form is shown below:
+Define \(y_i\) as the estimated level of happiness. Then \(\beta_0\)
+would be the estimated level of happiness given that all other variables
+are zero, \(\beta_i\) would be the respective effects on estimated
+levels of happiness for each of our variables. The full model form is
+shown below:
 
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
+package of Goodrich et al. (2022). We use the default priors from
+\texttt{rstanarm}.
 
-## Model justification
+\hypertarget{model-justification}{%
+\subsection{Model justification}\label{model-justification}}
 
-In our study, we employ a multiple regression model to predict happiness levels using the World Values Survey data.
-Given that happiness is influenced by a diverse range of factors, a model that can handle multiple regressors is critical in understanding the relationship with variables such as government surveillance acceptance, email monitoring acceptance, information collection acceptance, and happiness.
-Furthermore, the model allows us to isolate the unique contributions of each predictor to happiness.
+In our study, we employ a multiple regression model to predict happiness
+levels using the World Values Survey data. Given that happiness is
+influenced by a diverse range of factors, a model that can handle
+multiple regressors is critical in understanding the relationship with
+variables such as government surveillance acceptance, email monitoring
+acceptance, information collection acceptance, and happiness.
+Furthermore, the model allows us to isolate the unique contributions of
+each predictor to happiness.
 
-Our large sample size—approximately 3000 respondents—strengthens the model further.
-A robust sample size ensures that our parameter estimates are reliable and reduces the likelihood of statistical errors.
-It also increases the generalizability of our findings, ensuring that our conclusions are not just applicable to a narrow subset of the population but can be extended to China as a whole.
-Additionally, a larger dataset supports the complexity of our model, allowing us to include multiple predictors without the risk of overfitting, thereby maintaining the model’s integrity and robustness.
-The overall statistical significance of our test will be examined further later in this study.
+Our large sample size---approximately 3000 respondents---strengthens the
+model further. A robust sample size ensures that our parameter estimates
+are reliable and reduces the likelihood of statistical errors. It also
+increases the generalizability of our findings, ensuring that our
+conclusions are not just applicable to a narrow subset of the population
+but can be extended to China as a whole. Additionally, a larger dataset
+supports the complexity of our model, allowing us to include multiple
+predictors without the risk of overfitting, thereby maintaining the
+model's integrity and robustness. The overall statistical significance
+of our test will be examined further later in this study.
 
-# Results {@sec-results}
+\hypertarget{results-sec-results}{%
+\section{\texorpdfstring{Results
+\{\textbf{?@sec-results}\}}{Results \{?@sec-results\}}}\label{results-sec-results}}
 
-Our results are summarized in @tbl-modelresults.
+Our results are summarized in Table~\ref{tbl-modelresults}.
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
+\hypertarget{tbl-modelresults}{}
+\begin{table}
+\caption{\label{tbl-modelresults}Regression Model Results for Predicting Happiness Based on Government
+Perceptions and Age }\tabularnewline
 
-happiness_model <- readRDS(here(file = "models/happiness_model.rds"))
-```
+\centering
+\begin{tabular}[t]{lc}
+\toprule
+  & (1)\\
+\midrule
+(Intercept) & \num{7.23}\\
+ & (\num{0.21})\\
+Government\_Surveillance & \num{-0.06}\\
+ & \vphantom{1} (\num{0.05})\\
+Email\_Monitoring & \num{0.00}\\
+ & (\num{0.05})\\
+Information\_Collection & \num{-0.01}\\
+ & (\num{0.04})\\
+National\_Pride & \num{-0.50}\\
+ & (\num{0.06})\\
+age & \num{0.02}\\
+ & (\num{0.00})\\
+Government\_Responsibility & \num{0.05}\\
+ & (\num{0.01})\\
+\midrule
+Num.Obs. & \num{2950}\\
+R2 & \num{0.054}\\
+R2 Adj. & \num{0.048}\\
+Log.Lik. & \num{-6186.433}\\
+ELPD & \num{-6193.8}\\
+ELPD s.e. & \num{44.4}\\
+LOOIC & \num{12387.7}\\
+LOOIC s.e. & \num{88.8}\\
+WAIC & \num{12387.7}\\
+RMSE & \num{1.97}\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Regression Model Results for Predicting Happiness Based on Government Perceptions and Age"
-#| warning: false
+The regression analysis presented in Table~\ref{tbl-modelresults}
+reveals an expected baseline happiness level of 7.60, as indicated by
+the model's intercept. This suggests a generally positive baseline level
+of happiness among respondents when all other variables are held
+constant. The coefficients for the support for government surveillance,
+email monitoring, and information collection are slightly negative, at
+-0.06, -0.01, and -0.01 respectively, suggesting a marginal decrease in
+happiness scores associated with increased acceptance of these
+governance measures. Notably, national pride shows a stronger negative
+association with happiness, with a coefficient of -0.50, indicating a
+significant decrease in happiness as national pride increases. In
+contrast, the age coefficient of 0.02 suggests a slight increase in
+happiness with age.
 
-library(modelsummary)
-modelsummary::modelsummary(
-  happiness_model,
-  statistic = "mad",  
-  fmt = 2  
-)
-```
-The regression analysis presented in @tbl-modelresults reveals an expected baseline happiness level of 7.60, as indicated by the model's intercept.
-This suggests a generally positive baseline level of happiness among respondents when all other variables are held constant.
-The coefficients for the support for government surveillance, email monitoring, and information collection are slightly negative, at -0.06, -0.01, and -0.01 respectively, suggesting a marginal decrease in happiness scores associated with increased acceptance of these governance measures.
-Notably, national pride shows a stronger negative association with happiness, with a coefficient of -0.50, indicating a significant decrease in happiness as national pride increases.
-In contrast, the age coefficient of 0.02 suggests a slight increase in happiness with age.
+The model accounts for a modest 4.8\% of the variance in happiness
+scores, as reflected by an R-squared value of 0.048, implying that other
+unexamined factors may play a more substantial role in influencing
+happiness. The adjusted R-squared value, at 0.043, indicates a minimal
+increase in explanatory power when accounting for the number of
+predictors. Furthermore, the Root Mean Square Error (RMSE) of 1.98
+points to the model's prediction errors' standard deviation, signifying
+potential areas for model refinement. These results provide a
+statistical basis for the model's performance, emphasizing the nuanced
+challenge of predicting subjective well-being through perceived
+governance and age.
 
-The model accounts for a modest 4.8% of the variance in happiness scores, as reflected by an R-squared value of 0.048, implying that other unexamined factors may play a more substantial role in influencing happiness.
-The adjusted R-squared value, at 0.043, indicates a minimal increase in explanatory power when accounting for the number of predictors.
-Furthermore, the Root Mean Square Error (RMSE) of 1.98 points to the model's prediction errors' standard deviation, signifying potential areas for model refinement.
-These results provide a statistical basis for the model's performance, emphasizing the nuanced challenge of predicting subjective well-being through perceived governance and age.
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| label: fig-checks
-#| fig-cap: "Happiness Model Checks"
-library(rstanarm)
-library(bayesplot)
-library(ggplot2)
+\begin{figure}
 
-ppc_dens_overlay(y = wvsdata$Happiness, yrep = posterior_predict(happiness_model))
+{\centering \includegraphics{paper_files/figure-pdf/fig-checks-1.pdf}
 
-mcmc_trace(
-  as.array(happiness_model),
-  pars = c("(Intercept)", "Government_Surveillance", "Email_Monitoring", "Information_Collection", "National_Pride", "age", "Government_Responsibility")
-)
-```
-The posterior predictive check, visualized by @fig-checks, helps us evaluate the fit of our Bayesian model.
-By overlapping the observed happiness data with the simulated posterior predictive values, this plot illustrates how well our model reproduces the observed outcomes.
-The congruence between the values signifies that the model adequately captures the central tendency and variability of the actual happiness scores.
-Notably, if there are significant deviations it could indicate that the model may not fully account for the data's characteristics, prompting us to consider model refinements or additional predictors.
+}
 
-The trace plot provides a representation of the Markov Chain Monte Carlo (MCMC) sampling process, essential for evaluating the convergence of the chains.
-Each parameter's trace, represented by individual lines for each chain, should display a "mixing" behavior, converging to and fluctuating around a common value, without exhibiting trends or periodicity.
-Such patterns indicate that the chains have reached a stationary distribution, and the samples drawn are likely from the true posterior distribution.
-If the chains do not converge, this implies that the sampling process has not yet adequately captured the full behaviour of the true distribution, and further iterations or model adjustments may be required to ensure reliable inference.
+\caption{\label{fig-checks-1}Happiness Model Checks}
 
-# Discussion {@sec-discussion}
+\end{figure}
 
-## Model Findings {#sec-first-point}
+\begin{figure}
 
-As shown in our @sec-results section, we found that the initial baseline measure for happiness in China was quite high, at a predicted level of 7.60 given all other variables are at zero.
-We discover that our results disagree with Helliwell and Putnam's (2004) findings where belief in government policies are positively correlated with well-being.
-Our model suggests that an increase in support for any of the three policies correlates with a slight decrease in overall happiness level.
-However, we find that although national pride is negatively correlated with our measure of happiness, once we factor in that national pride is measured on a scale of 1-5 with 1 being the highest, we realize that national pride is the largest indicator of happiness out of our chosen variables.
-This could be because we are exclusively looking at a population of Chinese citizens.
-It is expected that residents and citizens that do not pride themselves in being Chinese are generally less happy while they are living there.
-Furthermore, we see a very slight positive coefficient for our age variable, suggesting that as Chinese citizens grow, they become more satisfied with their life.
-This could be potentially attributed to the stressful career and educational lifestyle of China.
-With a culture of overworking compounded with the pressure of the Gaokao, young citizens may experience lower levels of overall happiness compared to the older generation.
+{\centering \includegraphics{paper_files/figure-pdf/fig-checks-2.pdf}
 
-From our results, we see that even with growing discontentment towards China in the Western world, national pride and happiness levels seem to be unhindered and remain reasonably high.
-Yet, we also notice support for overreaching government policies with regards to surveillance and monitoring does not correlate with the high levels of national pride.
-Therefore, it is reasonable to conclude that although most Chinese citizens are very proud of their nationality, that does not necessarily correspond with support for the actions of the government.
+}
 
-## Weaknesses and next steps
+\caption{\label{fig-checks-2}Happiness Model Checks}
 
-With an R-squared value of 0.048, it seems that an incredibly small amount of variance is explained by our model.
-This is most likely due to omitted variable bias, where we neglected to include several other important factors when developing our regression model.
-Therefore, it is very likely that our chosen variables on support for government policies and/or national pride are not that significant in predicting overall happiness level.
-However, when considering the fact that the original questionnaire contained approximately 300 questions, it is to be expected that there would be a lot of unaccounted for variance in our data.
-Perhaps stronger expected indicators of overall happiness would consist marital status, annual income, and employment status.
-With regards to our model, we would likely get a more accurate regression by including more questions.
-However, due to the incredibly large amount of questions and responses, this could lead to overfitting.
-Although the adjusted R-squared value accounts partly for too many regressors, there is no feasible way to run a Bayesian regression model on all 300 questions.
-Therefore, future iterations of this study could look at combining several values into one.
-For example, support for government surveillance could be combined into one variable instead of three separate ones.
-Furthermore, questions that seem to have no impact on happiness level could also be ommitted by user discretion.
+\end{figure}
 
-Future research may also consist of comparisons between different nations that partook in the World Values Survey.
-Specifically, comparisons for national pride and government support between communist and democratic countries may lead to interesting inferences on the societal beliefs for their respective nations.
-A heavier reliance on governmental structures in a communist society may lead to higher levels of national pride when compared to less reliant democratic nations.
+The posterior predictive check, visualized by \textbf{?@fig-checks},
+helps us evaluate the fit of our Bayesian model. By overlapping the
+observed happiness data with the simulated posterior predictive values,
+this plot illustrates how well our model reproduces the observed
+outcomes. The congruence between the values signifies that the model
+adequately captures the central tendency and variability of the actual
+happiness scores. Notably, if there are significant deviations it could
+indicate that the model may not fully account for the data's
+characteristics, prompting us to consider model refinements or
+additional predictors.
+
+The trace plot provides a representation of the Markov Chain Monte Carlo
+(MCMC) sampling process, essential for evaluating the convergence of the
+chains. Each parameter's trace, represented by individual lines for each
+chain, should display a ``mixing'' behavior, converging to and
+fluctuating around a common value, without exhibiting trends or
+periodicity. Such patterns indicate that the chains have reached a
+stationary distribution, and the samples drawn are likely from the true
+posterior distribution. If the chains do not converge, this implies that
+the sampling process has not yet adequately captured the full behaviour
+of the true distribution, and further iterations or model adjustments
+may be required to ensure reliable inference.
+
+\hypertarget{discussion-sec-discussion}{%
+\section{\texorpdfstring{Discussion
+\{\textbf{?@sec-discussion}\}}{Discussion \{?@sec-discussion\}}}\label{discussion-sec-discussion}}
+
+\hypertarget{sec-first-point}{%
+\subsection{Model Findings}\label{sec-first-point}}
+
+As shown in our \textbf{?@sec-results} section, we found that the
+initial baseline measure for happiness in China was quite high, at a
+predicted level of 7.60 given all other variables are at zero. We
+discover that our results disagree with Helliwell and Putnam's (2004)
+findings where belief in government policies are positively correlated
+with well-being. Our model suggests that an increase in support for any
+of the three policies correlates with a slight decrease in overall
+happiness level. However, we find that although national pride is
+negatively correlated with our measure of happiness, once we factor in
+that national pride is measured on a scale of 1-5 with 1 being the
+highest, we realize that national pride is the largest indicator of
+happiness out of our chosen variables. This could be because we are
+exclusively looking at a population of Chinese citizens. It is expected
+that residents and citizens that do not pride themselves in being
+Chinese are generally less happy while they are living there.
+Furthermore, we see a very slight positive coefficient for our age
+variable, suggesting that as Chinese citizens grow, they become more
+satisfied with their life. This could be potentially attributed to the
+stressful career and educational lifestyle of China. With a culture of
+overworking compounded with the pressure of the Gaokao, young citizens
+may experience lower levels of overall happiness compared to the older
+generation.
+
+From our results, we see that even with growing discontentment towards
+China in the Western world, national pride and happiness levels seem to
+be unhindered and remain reasonably high. Yet, we also notice support
+for overreaching government policies with regards to surveillance and
+monitoring does not correlate with the high levels of national pride.
+Therefore, it is reasonable to conclude that although most Chinese
+citizens are very proud of their nationality, that does not necessarily
+correspond with support for the actions of the government.
+
+\hypertarget{weaknesses-and-next-steps}{%
+\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}}
+
+With an R-squared value of 0.048, it seems that an incredibly small
+amount of variance is explained by our model. This is most likely due to
+omitted variable bias, where we neglected to include several other
+important factors when developing our regression model. Therefore, it is
+very likely that our chosen variables on support for government policies
+and/or national pride are not that significant in predicting overall
+happiness level. However, when considering the fact that the original
+questionnaire contained approximately 300 questions, it is to be
+expected that there would be a lot of unaccounted for variance in our
+data. Perhaps stronger expected indicators of overall happiness would
+consist marital status, annual income, and employment status. With
+regards to our model, we would likely get a more accurate regression by
+including more questions. However, due to the incredibly large amount of
+questions and responses, this could lead to overfitting. Although the
+adjusted R-squared value accounts partly for too many regressors, there
+is no feasible way to run a Bayesian regression model on all 300
+questions. Therefore, future iterations of this study could look at
+combining several values into one. For example, support for government
+surveillance could be combined into one variable instead of three
+separate ones. Furthermore, questions that seem to have no impact on
+happiness level could also be ommitted by user discretion.
+
+Future research may also consist of comparisons between different
+nations that partook in the World Values Survey. Specifically,
+comparisons for national pride and government support between communist
+and democratic countries may lead to interesting inferences on the
+societal beliefs for their respective nations. A heavier reliance on
+governmental structures in a communist society may lead to higher levels
+of national pride when compared to less reliant democratic nations.
 
@@
 
-# Appendix {@sec-appendix}
+\hypertarget{appendix-sec-appendix}{%
+\section{\texorpdfstring{Appendix
+\{\textbf{?@sec-appendix}\}}{Appendix \{?@sec-appendix\}}}\label{appendix-sec-appendix}}
 
-```{r}
-#| echo: false
-#| warning: false
-#| fig-cap: "Support for Surveillance, Email Monitoring, and Information Collection by Age Group"
-#| label: fig-compiled
-#| fig.width: 6
-library(ggplot2)
-library(dplyr)
+\begin{figure}
 
-long_data <- wvsdata %>%
-  select(Age_Group, Government_Surveillance, Email_Monitoring, Information_Collection, National_Pride, Government_Responsibility) %>%
-  pivot_longer(cols = c(Government_Surveillance, Email_Monitoring, Information_Collection, National_Pride, Government_Responsibility), 
-               names_to = "Variable", values_to = "Value")
+{\centering \includegraphics{paper_files/figure-pdf/fig-compiled-1.pdf}
 
-# Plotting the responses for Government_Surveillance, Email_Monitoring, Information_Collection, and National Pride across different age groups
-ggplot(long_data, aes(x = Age_Group, fill = as.factor(Value))) +
-  geom_bar(position = "dodge") +
-  facet_wrap(~ Variable, scales = "free_y") +  # Allows each facet to independently scale the y-axis
-  scale_fill_brewer(palette = "Set2") +  # Using the "Set2" color palette for better aesthetics
-  labs(title = "Support for Surveillance, Email Monitoring, Information Collection, Government Responsibility, and National Pride by Age Group",
-       x = "Age Group",
-       y = "Count",
-       fill = "Response Level") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-        strip.text = element_text(size = 8))
-```
+}
+
+\caption{\label{fig-compiled}Support for Surveillance, Email Monitoring,
+and Information Collection by Age Group}
+
+\end{figure}
 
@@
 
-# References
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-rstanarm}{}}%
+Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
+{``Rstanarm: {Bayesian} Applied Regression Modeling via {Stan}.''}
+\url{https://mc-stan.org/rstanarm/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-citeR}{}}%
+R Core Team. 2023. \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}.
+
+\end{CSLReferences}
+
+\end{document}

### 2024-04-23 scripts/04-model.R

@@ -13,25 +13,21 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+wvsdata <- read_parquet(here("data/analysis_data/analysis_data2018.parquet"))
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
-
-
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+happiness_model <- stan_glm(
+  Happiness ~ Government_Surveillance + Email_Monitoring + Information_Collection + National_Pride + age + Government_Responsibility,
+  data = wvsdata,
+  family = gaussian(),
+  prior = normal(0, 2.5),
+  prior_intercept = normal(0, 2.5),
+  prior_aux = exponential(1),
+  chains = 4,
+  iter = 2000,
+  seed = 123456,
+  refresh = 0
 )
 
+# Optionally, save your model for future use
+saveRDS(happiness_model, file = here::here("models/happiness_model.rds"))
 

### 2024-04-23 paper/paper.qmd
please render

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "In this study, we employed a multiple regression model to analyze the impact of government surveillance, email monitoring, information collection, national pride, and age on happiness levels using data from the World Values Survey.
+The findings indicate that higher levels of government surveillance and email monitoring are slightly negatively associated with happiness, whereas higher levels of national pride shows a strong positive relationship with happiness levels.
+Furthermore, age was positively correlated with happiness, suggesting that older individuals tend to report higher levels of well-being."
 format: pdf
@@
 #| fig-cap: Summary Statistics for World Values Survey
-library(knitr)
-library(kableExtra)
-library(dplyr)
-library(tidyr)
-
 variables_of_interest <- c("National_Pride", "Happiness", "Government_Surveillance", 
@@
 summary_stats_long <- summary_stats %>%
-  pivot_longer(cols = everything(), names_to = c("Variable", "Statistic"), names_pattern = "(.+)_(Mean|SD|Median|Q1|Q3|Min|Max)")
+  pivot_longer(
+    cols = everything(),
+    names_to = c("Variable", "Statistic"),
+    names_pattern = "(.+)_(.+)"
+  )
 
-summary_stats_wide <- summary_stats_long %>%
-  pivot_wider(names_from = Statistic, values_from = value)
-
-summary_table <- kable(summary_stats_wide, format = "latex", booktabs = TRUE, 
-                       caption = "Descriptive Statistics for Selected Variables") %>%
-  row_spec(0, bold = TRUE)
-
-summary_table
+# Check the output
+print(summary_stats_long)
 ```
@@
 
-# Model {@sec-model}
+# Model {#sec-model}
 
@@
 
-# Results {@sec-results}
+# Results {#sec-results}
 
@@
 #| label: fig-checks
-#| fig-cap: "Happiness Model Checks"
+#| fig-cap: "Happiness Model Posterior Predictive Check"
 library(rstanarm)
@@
 ppc_dens_overlay(y = wvsdata$Happiness, yrep = posterior_predict(happiness_model))
-
+```
+The posterior predictive check, visualized by @fig-checks, helps us evaluate the fit of our Bayesian model.
+By overlapping the observed happiness data with the simulated posterior predictive values, this plot illustrates how well our model reproduces the observed outcomes.
+The congruence between the values signifies that the model adequately captures the central tendency and variability of the actual happiness scores.
+Notably, if there are significant deviations it could indicate that the model may not fully account for the data's characteristics, prompting us to consider model refinements or additional predictors.
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| label: fig-trace
+#| fig-cap: MCMC Trace Plot
+library(rstanarm)
+library(bayesplot)
+library(ggplot2)
 mcmc_trace(
@@
 ```
-The posterior predictive check, visualized by @fig-checks, helps us evaluate the fit of our Bayesian model.
-By overlapping the observed happiness data with the simulated posterior predictive values, this plot illustrates how well our model reproduces the observed outcomes.
-The congruence between the values signifies that the model adequately captures the central tendency and variability of the actual happiness scores.
-Notably, if there are significant deviations it could indicate that the model may not fully account for the data's characteristics, prompting us to consider model refinements or additional predictors.
 
-The trace plot provides a representation of the Markov Chain Monte Carlo (MCMC) sampling process, essential for evaluating the convergence of the chains.
+The trace plot shown in @fig-trace provides a representation of the Markov Chain Monte Carlo (MCMC) sampling process, essential for evaluating the convergence of the chains.
 Each parameter's trace, represented by individual lines for each chain, should display a "mixing" behavior, converging to and fluctuating around a common value, without exhibiting trends or periodicity.
@@
 
-# Discussion {@sec-discussion}
+# Discussion {#sec-discussion}
 
@@
 
-# Appendix {@sec-appendix}
+# Appendix {#sec-appendix}
 

### 2024-04-23 paper/paper.qmd
please

@@
 library(kableExtra)
+library(dplyr)
 wvsdata <- read_parquet(here("data/analysis_data/analysis_data2018.parquet"))
@@
 Studies present mixed views on the effects of socialism and democracy.
-Cheung and Leung (2007) found that collectivism significantly impacts the well-being of the Chinese, whereas Hofstede (1980) observed that individualism encourages economic growth.
-Moore (2005) argued that the freedoms introduced in the 1980s led the Chinese towards a strong form of individualism, which starkly contrasts with the collectivist approach of the Cultural Revolution.
-Steele and Lynch examined whether individualist or collectivist traits prevail in modern China and their impact on subjective well-being (SWB).
+Cheung and Leung found that collectivism significantly impacts the well-being of the Chinese, whereas Hofstede (1980) observed that individualism encourages economic growth [@hofstede][@cheung].
+Moore (2005) argued that the freedoms introduced in the 1980s led the Chinese towards a strong form of individualism, which starkly contrasts with the collectivist approach of the Cultural Revolution [@moore].
+Steele and Lynch examined whether individualist or collectivist traits prevail in modern China and their impact on subjective well-being (SWB) [@steele].
 They focused on how these orientations predict SWB and if their influence has shifted as China transitioned towards a market economy.
 
-While Steele and Lynch researched the impacts of the reform, this paper will attempt to reframe their ideas with a focus on the impacts of COVID-19.
-This study will replicate and extend Steele and Lynch’s previous research by examining the prevailing sentiments—individualist versus collectivist—in China post-COVID-19 in 2022 and their implications for SWB.
+While Steele and Lynch researched the impacts of the reform, this paper will attempt to reframe their ideas with a focus on the recent developments in China.
+This study will extend Steele and Lynch’s previous research by examining the prevailing sentiments—individualist versus collectivist—in China in 2022 and their implications for SWB.
 We analyze whether and how the relationship between these cultural orientations and well-being has evolved in the context of China's continued economic and social transformations.
@@
 
-Our investigation was conducted using the programming language R [@citeR], with the packages [@tidyverse], and [@dplyr]
-
-Although each of the variables have a different scale, the summary statistics of the current dataset can be seen in @fig-summary
+Our investigation was conducted using the programming language R [@citeR], with the packages [@tidyverse], [@arrow], [@model], [@here], [@kable] and [@dplyr].
+Techniques for some analysis methods were taken from [@rohan].
 
@@
 #| echo: false
-#| label: fig-summary
-#| fig-cap: Summary Statistics for World Values Survey
-variables_of_interest <- c("National_Pride", "Happiness", "Government_Surveillance", 
-                           "Email_Monitoring", "Information_Collection", 
-                           "Government_Responsibility", "age")
-
-summary_stats <- wvsdata %>%
-  summarise(across(all_of(variables_of_interest), list(
-    Mean = ~round(mean(.x, na.rm = TRUE), 2),
-    SD = ~round(sd(.x, na.rm = TRUE), 2),
-    Median = ~median(.x, na.rm = TRUE),
-    Q1 = ~quantile(.x, probs = 0.25, na.rm = TRUE),
-    Q3 = ~quantile(.x, probs = 0.75, na.rm = TRUE),
-    Min = ~min(.x, na.rm = TRUE),
-    Max = ~max(.x, na.rm = TRUE)
-  ), .names = "{.col}_{.fn}"))
-
-summary_stats_long <- summary_stats %>%
-  pivot_longer(
-    cols = everything(),
-    names_to = c("Variable", "Statistic"),
-    names_pattern = "(.+)_(.+)"
+#| cap: "Summary Statistics for World Values Survey"
+summary_stats <- data.frame(
+  Mean = round(apply(wvsdata, 2, mean, na.rm = TRUE), 2),   # Calculate mean, ignoring NA values and round to 2 decimals
+  StdDev = round(apply(wvsdata, 2, sd, na.rm = TRUE), 2),   # Calculate standard deviation, ignoring NA values and round to 2 decimals
+  Min = round(apply(wvsdata, 2, min, na.rm = TRUE), 2),     # Calculate minimum, ignoring NA values and round to 2 decimals
+  Max = round(apply(wvsdata, 2, max, na.rm = TRUE), 2),     # Calculate maximum, ignoring NA values and round to 2 decimals
+  IQR = round(apply(wvsdata, 2, IQR, na.rm = TRUE), 2)      # Calculate interquartile range, ignoring NA values and round to 2 decimals
 )
 
-# Check the output
-print(summary_stats_long)
+# Print the summary statistics table
+print(summary_stats)
 ```
 
-Initial observations of the summary statistics reveal that the mean happiness level is quite high, averaging to approximately 7.42 as opposed to the expected 5.
+Initial observations of the summary statistics in the table above reveals that the mean happiness level is quite high, averaging to approximately 7.42 as opposed to the expected 5.
 Furthermore, we see that the median level of happiness is 8, significantly higher than expected.
@@
 
-Before we develop our model, we have to assume that there is a relationship between our variables and happiness level.
-Research consistently indicates that the trust in, and perception of, governmental and societal systems significantly influences personal well-being (Helliwell & Putnam, 2004).
+Before we develop our model, we have to assume that there is a linear relationship between our variables and happiness level.
+Research consistently indicates that the trust in, and perception of, governmental and societal systems significantly influences personal well-being [@putnam].
 We postulate that individuals’ responses to questions about governance and privacy are not merely reflective of their current state but are shaped by their broader socio-political environment and personal experiences.
-Therefore, a person's level of happiness is not only a function of their immediate circumstances but also a reflection of their interactions with the societal and political structures they inhabit (Bjørnskov, 2006).
+Therefore, a person's level of happiness is not only a function of their immediate circumstances but also a reflection of their interactions with the societal and political structures they inhabit [@bjornskov].
 
@@
 Furthermore, cultural factors could moderate the relationship between governance attitudes and happiness.
-For example, in societies where collective well-being is emphasized, the acceptance of surveillance measures might correlate differently with happiness compared to societies that prioritize individual autonomy (Oishi, Diener, & Lucas, 2007).
+For example, in societies where collective well-being is emphasized, the acceptance of surveillance measures might correlate differently with happiness compared to societies that prioritize individual autonomy [@lucas].
 We expect that the effects for the government policies and age to be positive, while national pride is negative.
@@
 \begin{align} 
-y_i &= \beta_0 + \beta_1 \cdot \text{Gov Surveillance}_i + \beta_2 \cdot \text{Email Monitoring}_i + \beta_3 \cdot \text{Info Collection}_i + \beta_4 \cdot \text{Age}_i + \beta_5 \cdot \text{National Pride}_i + \text{Government Responsibility}_i + \epsilon_i
+y_i &= \beta_0 + \beta_1 \cdot \text{Gov Surveillance}_i + \beta_2 \cdot \text{Email Monitoring}_i + \beta_3 \cdot \text{Info Collection}_i
++ \beta_4 \cdot \text{Age}_i + \beta_5 \cdot \text{National Pride}_i + \text{Government Responsibility}_i + \epsilon_i
 \end{align}
@@
 
-In our study, we employ a multiple regression model to predict happiness levels using the World Values Survey data.
+In our study, we employ a Bayesian regression model to predict happiness levels using the World Values Survey data.
 Given that happiness is influenced by a diverse range of factors, a model that can handle multiple regressors is critical in understanding the relationship with variables such as government surveillance acceptance, email monitoring acceptance, information collection acceptance, and happiness.
 Furthermore, the model allows us to isolate the unique contributions of each predictor to happiness.
+We specifically chose a Bayesian regression model as opposed to other forms of regression, such as a Poisson.
+This is because a Poisson regression assumes that the variance of the dependent variable is equal to its mean, which restricts its application to data where this condition naturally holds.
+From our summary statistics in @sec-data, we see that this assumption does not hold.
 

### 2024-04-23 other/datasheet/datasheet_template.qmd
fixed summary statistic, knitr was not working please

---
title: "Datasheet for 'A dataset'"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset seeks to help scientists and policy makers understand changes in the beliefs, values and motivations of people throughout the world. 
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was created by the World Values Survey, which is governed by the Executive Committee, Scientific Advisory Committee, and the General Assembly of the United States
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - Numerous funds around the world like the Bill and Melinda Gates Foundation, the World Bank, and the University of Stockholm among others.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- People
2. *How many instances are there in total (of each type, if appropriate)?*
	- n/a
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- Very large sample of entire countries, random sampling was used but rural populations were also contacted
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Identifier and values for responses
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Identifier
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- No, although there were non-responses
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- No
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- n/a
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Very isolated communities may be hard to contact
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- Self contained
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- Yes, political beliefs should be confidential 
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- Potentially, political beliefs and personal values are asked.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- Yes, questions about martial status, age, gender, are all contained in the dataset
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- Yes, many of the above

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- Face-to-face interviews
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Pen and paper
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- Random probability sampling
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Volunteers
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- 2018-2022
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Yes, unknown
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- Obtained from the World Values Survey
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Yes, they were contacted asking if they wanted to participate in the survey
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Yes, it was one of the first questions in the survey
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Unknown
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Yes, several publications are listed on the World Values Survey website

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, empty values were removed
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- Yes
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- Yes, RStudio and R

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Yes, all published papers are available on the World Values Survey website
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- n/a
3. *What (other) tasks could the dataset be used for?*
	- n/a
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- Probably not
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- Discriminatory behaviours

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- No
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- World Values Survey website
3. *When will the dataset be distributed?*
	- Already released
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- Unknown
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- Not for the public dataset

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- World Values Survey
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Through the website
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- No, 2022 was the last wave
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- Yes, unknown
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Yes, maintained on the website but the dataset is no longer updated
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Such a large dataset I do not believe it is possible

\newpage

# References

### 2024-04-23 paper/paper.qmd
fixed summary statistic, knitr was not working please

@@
 ---
-title: "Pursuit of Happiness: The impact of growing Western criticism on Chinese Wellbeing"
+title: "Pursuit of Happiness: The impact of authoritarian government policies on Chinese well-being"
 author: 
@@
 date-format: long
-abstract: "In this study, we employed a multiple regression model to analyze the impact of government surveillance, email monitoring, information collection, national pride, and age on happiness levels using data from the World Values Survey.
+abstract: "In this study, we employed a Bayesian regression model to analyze the impact of government surveillance, email monitoring, information collection, national pride, and age on happiness levels using data from the World Values Survey.
 The findings indicate that higher levels of government surveillance and email monitoring are slightly negatively associated with happiness, whereas higher levels of national pride shows a strong positive relationship with happiness levels.
-Furthermore, age was positively correlated with happiness, suggesting that older individuals tend to report higher levels of well-being."
+Furthermore, age was positively correlated with happiness, suggesting that older individuals tend to report higher levels of well-being.
+Our results illustrate how support for several authoritarian governmental policies may impact overall well-being in a socialist nation."
 format: pdf
@@
 The 1990s market reforms aimed to control capitalism, showing that socialism could harness capitalist growth to increase national power.
-Today, China is a global economic leader, second only to the US in GDP; however, it is essential to assess how these changes affect societal well-being.
+Today, China is a global economic leader, second only to the US in GDP; however, it is essential to assess how these rapid changes affect societal well-being.
 Studies present mixed views on the effects of socialism and democracy.
@@
 Moore (2005) argued that the freedoms introduced in the 1980s led the Chinese towards a strong form of individualism, which starkly contrasts with the collectivist approach of the Cultural Revolution [@moore].
-Steele and Lynch examined whether individualist or collectivist traits prevail in modern China and their impact on subjective well-being (SWB) [@steele].
+Our study will reassess a previous paper by Steele and Lynch, who examined whether individualist or collectivist traits prevail in modern China and their impact on subjective well-being (SWB) [@steele].
 They focused on how these orientations predict SWB and if their influence has shifted as China transitioned towards a market economy.
@@
 While Steele and Lynch researched the impacts of the reform, this paper will attempt to reframe their ideas with a focus on the recent developments in China.
-This study will extend Steele and Lynch’s previous research by examining the prevailing sentiments—individualist versus collectivist—in China in 2022 and their implications for SWB.
-We analyze whether and how the relationship between these cultural orientations and well-being has evolved in the context of China's continued economic and social transformations.
+This study will extend Steele and Lynch’s previous research by examining the prevailing sentiments—individualist versus collectivist—in China in the past few years and their implications for SWB.
+We analyze whether the relationship between these cultural orientations and well-being has evolved in the context of China's continued economic and social transformations.
 
@@
 
-To replicate the paper by Steele and Lynch, we obtained our data from the World Values Survey.
+To continue our paper based on Steele and Lynch, we obtained our data from the World Values Survey.
+The World Values Survey is the largest non-commercial international investigation of human values ever executed.
+There are no other datasets of a similar size that target human beliefs and opinions.
 While Steele and Lynch used time series data from three surveys (1990, 2001, 2007), we aim to look at more recent trends so we will include the World Values Survey data obtained from their 2018 wave.
@@
 Although the sample for China was chosen through random sampling, survey guidelines dictated that there would be no replacement for non-responses.
-Therefore, missing data would have to be parsed out.
+Therefore, missing data had to be parsed out.
 
@@
 
-Our investigation was conducted using the programming language R [@citeR], with the packages [@tidyverse], [@arrow], [@model], [@here], [@kable] and [@dplyr].
-Techniques for some analysis methods were taken from [@rohan].
+Our investigation was conducted using the programming language R [@citeR], with the packages tidyverse [@tidyverse], arrow [@arrow], modelsummary [@model], here [@here], kable [@kable] and dplyr [@dplyr].
+Techniques for some analysis methods were taken from Telling Stories with Data [@rohan].
 
@@
 Initial observations of the summary statistics in the table above reveals that the mean happiness level is quite high, averaging to approximately 7.42 as opposed to the expected 5.
-Furthermore, we see that the median level of happiness is 8, significantly higher than expected.
 We also notice that national pride is very high, with a mean of 1.64.
@@
 
-We can also see the distribution for each of our variables in @fig-distgraphs:
+The distribution for each of our variables is depicted in @fig-distgraphs:
 
@@
 Furthermore, the dataset provides information on how responses to question differ based off age.
-From this, we can depict how different age groups tend to respond to questions.
+From this, we can visualize how different age groups tend to respond to questions.
 For example, we expect the younger generation to be more progressive, leading to higher disapproval rates for government surveillance policies.
@@
 As the question asks about government surveillance in public areas, we can potentially infer citizens may oppose government email/information supervision as those are more private.
-However, as seen in @fig-compiled, we notice that the support for the collection of information for anybody in China is significantly higher than the other variables.
+However, as seen in @fig-compiled, we notice that the support for the collection of information for anyone in China is significantly higher than the other variables.
 
@@
 
-The potential of using the World Values Survey data to predict happiness is based on the idea that certain key variables, such as attitudes towards governance and societal structures, are able to predict an individual’s level of happiness.
+Using the World Values Survey data to predict happiness is based on the idea that certain key variables, such as attitudes towards governance and societal structures, are able to predict an individual’s level of happiness.
 Our model will hopefully be able to show how and if specific perceptions on government surveillance acceptance, email monitoring, and information collection are indicative of broader societal satisfaction.
@@
 \begin{align} 
-y_i &= \beta_0 + \beta_1 \cdot \text{Gov Surveillance}_i + \beta_2 \cdot \text{Email Monitoring}_i + \beta_3 \cdot \text{Info Collection}_i
-+ \beta_4 \cdot \text{Age}_i + \beta_5 \cdot \text{National Pride}_i + \text{Government Responsibility}_i + \epsilon_i
+y_i &= \beta_0 + \beta_1 \cdot \text{Gov Surveillance}_i + \beta_2 \cdot \text{Email Monitoring}_i + \beta_3 \cdot \text{Info Collection}_i\\
++ \beta_4 \cdot \text{Age}_i + \beta_5 \cdot \text{Pride}_i + \text{Gov Responsibility}_i + \epsilon_i
 \end{align}
@@
 
+## Ethical Considerations
+
+In conducting research that delves into personal beliefs and societal norms, such as happiness, national pride, and government surveillance acceptance, it is essential to consider ethical ramifications.
+The sensitive nature of questions related to government surveillance and monitoring requires careful deliberation.
+Collecting data on these topics might cause discomfort or fear among respondents, particularly in regions where government criticism is not tolerated openly.
+This necessitates stringent measures to ensure anonymity and confidentiality of the survey responses to protect participants from any possible repercussions.
+
+Moreover, given the potential for such research to influence public opinion and policy, it is crucial to handle data interpretation and dissemination with integrity.
+Researchers must be vigilant against biases in data analysis and reporting, striving for objectivity and transparency in their methodologies and findings.
+Acknowledging the limitations and subjective interpretations inherent in the study is also essential to prevent misrepresentation of the data and to maintain the trustworthiness of the research.
+
+Additionally, the study's potential impact on participants and broader societal implications should be considered.
+Research findings, particularly those that may portray certain groups in a negative light or suggest discontent with governmental policies, could have consequences if used inappropriately or taken out of context.
+As such, it is the responsibility of the researchers to ensure that the conclusions drawn are balanced, contextual, and do not contribute to stigmatization or discrimination against any group.
+
 ## Weaknesses and next steps
@@
 
-Future research may also consist of comparisons between different nations that partook in the World Values Survey.
+Another source of error is the subjective nature of these variables, as they are deeply influenced by individual experiences, cultural contexts, and personal biases.
+These factors can affect both how questions are perceived by respondents and how their responses are interpreted by researchers.
+For instance, the concept of "national pride" may carry different connotations and importance in different cultural or political contexts, potentially skewing responses based on the respondent's background or current political climate.
+"Happiness" and current "life satisfaction" are also subjective measures and the same point value provided by two different respondents is likely to have different meanings for each of them.
+
+Future research may consist of comparisons between different nations that partook in the World Values Survey.
 Specifically, comparisons for national pride and government support between communist and democratic countries may lead to interesting inferences on the societal beliefs for their respective nations.
 A heavier reliance on governmental structures in a communist society may lead to higher levels of national pride when compared to less reliant democratic nations.
+
+Following Steele and Lynch's original research method, variations between waves of the World Values Survey may be dealt with by combining several responses into one variable.
+Although this leads to higher variance and may change end results, the value gained from analyzing temporal trends may outweigh these risks.
+With our original research goal in mind, the change in perception of China may be analyzed throughout the past two decades to determine if the rapid onset of anti-CCP material impacts citizen responses in any way.
 

### 2024-04-23 scripts/00-simulate_data.R

@@ -1,19 +1,32 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates data obtained for World Values Survey
+# Author: Alexander Sun
+# Date: April 21st 2024
+# Contact: alexander.sun@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+set.seed(123)
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+
+# Generate simulation
+wvsdata_simulation <- tibble(
+  national_pride = rbinom(n = 3000, size = 5, prob = 0.6),  # National pride scores on a 0-5 scale
+  government_surveillance = rbinom(n = 3000, size = 4, prob = 0.5),  # Government surveillance scores on a 0-4 scale
+  email_monitoring = rbinom(n = 3000, size = 4, prob = 0.5),  # Email monitoring scores on a 0-4 scale
+  information_collection = rbinom(n = 3000, size = 4, prob = 0.5),  # Information collection scores on a 0-4 scale
+  happiness = rbinom(n = 3000, size = 10, prob = 0.5),  # Happiness scores on a 0-10 scale
+  age = sample(18:70, 3000, replace = TRUE)  # Age of respondents
+)
+
+head(wvsdata_simulation)
+
+summary(wvsdata_simulation)
+
+write_csv(wvsdata_simulation, "data/raw_data/wvsdata_simulated.csv")
+
 
 
 

### 2024-04-23 scripts/03-test_data.R

@@ -1,15 +1,34 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the generated simulated data
+# Author: Alexander Sun
+# Date: April 21st 2024
+# Contact: alexander.sun@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
-
+wvsdata_simulation <- read.csv("data/raw_data/wvsdata_simulated.csv")
 #### Test data ####
+all(wvsdata_simulation$national_pride >= 0) 
+all(wvsdata_simulation$government_surveillance >= 0)
+all(wvsdata_simulation$email_monitoring >= 0)
+all(wvsdata_simulation$information_collection >= 0)
+all(wvsdata_simulation$happiness >= 0)
+all(wvsdata_simulation$age >= 18 & wvsdata_simulation$age <= 70)
+all(wvsdata_simulation$national_pride <= 5)
+all(wvsdata_simulation$government_surveillance <= 4)
+all(wvsdata_simulation$email_monitoring <= 4)
+all(wvsdata_simulation$information_collection <= 4)
+all(wvsdata_simulation$happiness <= 10)
+
+#chisquare test to see if age is uniformly distributed
+chisq.test(table(cut(wvsdata_simulation$age, breaks = seq(17, 71, by = 1) - 0.5)))
+
+#check if mean and variance are reasonably close to expected values
+expected_mean_pride <- 5 * 0.6
+expected_variance_pride <- 5 * 0.6 * 0.4
+actual_mean_pride <- mean(wvsdata_simulation$national_pride)
+actual_variance_pride <- var(wvsdata_simulation$national_pride)
+abs(expected_mean_pride - actual_mean_pride) < 0.5
+abs(expected_variance_pride - actual_variance_pride) < 0.5

### 2024-04-23 paper/paper.qmd
please

@@
 This study will extend Steele and Lynch’s previous research by examining the prevailing sentiments—individualist versus collectivist—in China in the past few years and their implications for SWB.
-We analyze whether the relationship between these cultural orientations and well-being has evolved in the context of China's continued economic and social transformations.
+Specifically, we will analyze whether there is a relationship between these cultural orientations and well-being.
+
+Our findings indicate that citizens' support for authoritarian policies does not significantly affect their overall happiness.
+Conversely, national pride appears to have a much more substantial influence on happiness, suggesting that support for CCP policies may not be directly tied to nationalism.
 
 In this project, the estimand will be the difference in happiness level between each participant based on information like national pride, government support, and age.
+Given the increasing Western discontent with China, these findings could help mitigate xenophobia by highlighting the distinction between the Chinese government and its citizens.
 
@@
 There are no other datasets of a similar size that target human beliefs and opinions.
-While Steele and Lynch used time series data from three surveys (1990, 2001, 2007), we aim to look at more recent trends so we will include the World Values Survey data obtained from their 2018 wave.
+While Steele and Lynch used time series data from three surveys (1990, 2001, 2007), we aim to look at more recent trends so we will use the World Values Survey data obtained from their 2018 wave.
 To be included into the survey dataset, countries must meet a minimum of 1200 entries.
